\documentclass[12pt,a4paper]{article}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usetikzlibrary{shapes, arrows, positioning}

\usepackage{amsmath,amssymb,mdframed}
\setcounter{page}{2}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.5in}
\setlength{\headsep}{1cm}
\setlength{\textheight}{9.0in}

\begin{document}
Throughout, the following game is considered:

Users of an online messaging platform can choose one of two incompatible apps:
app $A$ or app $B$.  
The action set in this game is $\mathcal{A}=\{A, B\}$.

Each user gains a base level of utility from being able to send messages at all.
On top of this, their utility increases with the proportion of other users
choosing the same app (since it becomes easier to contact friends).

Considering a population vector $x=(x_1,1 - x_1)$ where $x_1$ is the proportion
of the population using app $A$, the fitness functions are:
\[
    f_A(x)=1+2x_1,
    \qquad
    f_B(x)=1+2(1-x_1).
\]

\begin{enumerate}
    \item Give an interpretation for the fitness functions.

    \item State the replicator dynamics equation for a population with two types.

    \item Define a stable population for the replicator dynamics.

    \item Define a post--entry population.

    \item Define an evolutionary stable strategy (ESS).

    \item Give the replicator dynamics equation for this game and obtain all stable populations.

    \item For each of the following initial populations of 
    $x\in\{(0.01, 0.99), (0.49,0.51), (0.99, 0.01)\}$, 
    calculate the first step of Euler's method of numerical integration with a 
    step size of $h=0.01$.  
    In each case offer an interpretation in terms of evolutionary stability.

    \item Now suppose that the strength of the coordination benefit is a parameter
      $a\neq 0$, so that
      \[
      f_A(x)=1+a x_1,
      \qquad
      f_B(x)=1+a(1-x_1).
      \]
      Derive the replicator dynamics for general $a$ and determine for which
      values of $a$ the mixed population $x^\star=(\tfrac12,\tfrac12)$ is
      evolutionarily stable.  
      Justify your answer.
\end{enumerate}
\end{document}
